### 2025-09-23 paper/sec/authoring-workflow.tex
50 mins.

\paragraph{Initial configuration.} The author initially imports the text and accompanying data into the
system, which creates a Fluid representation of the target document. Initially that representation is just a
string literal of the form \kw{"""..."""}, where the triple quotes are the Fluid syntax for an
\emph{interpolated string}, i.e.~a string literal where expressions of the form \kw{\{$e$\}} are permitted
within the string. The \SuggestionAgent analyses the inputs and identifies candidate fragments of natural
language which could be replaced by Fluid expressions.

\paragraph{Authoring workflow.} The system then enters the human-in-the loop authoring workflow shown in
Figure~\ref{fig:interpretation-agent}, where the author interacts with the \InterpretationAgent. The system
initially waits for the author to select a fragment of text $s$ to interpret, a fragment which may or may not
have been highlighted previously by the \SuggestionAgent. The system then generates a candidate Fluid
expression $e$ by prompting the LLM (\secref{prompt-design} below). The expression is validated through a
closed loop program synthesis step which checks that it is well-formed and evaluates to the target fragment
$s$. If this process succeeds, the system replaces the selected substring $s$ with the interpolation
expression \kw{\{$e$\}}, creating a new document configuration. This is the primary successful path through
the workflow and returns the system to the entry state where it is waiting for another top-level interaction
from the author.

>>>>

The high-level workflow is as follows:

\begin{enumerate}

\item \textbf{Initial configuration.} Author imports text and accompanying data into the system, creating a
programmatic representation of the target document. Initially this representation is isomorphic to the target
text, namely a string literal of the form \kw{"""..."""}, where the triple quotes are Fluid syntax for an
\emph{interpolated string}, i.e.~a string literal where expressions of the form \kw{\{$e$\}} are permitted
within the string. The \SuggestionAgent analyses these inputs and identifies any fragments of natural language
which are candidates for being computed instead of remaining as literal substrings.

\item \textbf{Authoring workflow.} The system then enters the human-in-the loop authoring workflow shown in
Figure~\ref{fig:interpretation-agent}, where the author interacts with the \InterpretationAgent. The system
initially waits for the author to select a fragment of text $s$ to interpret, a fragment which may or may not
have been highlighted previously by the \SuggestionAgent. The system then generates a candidate Fluid
expression $e$ by prompting the LLM (\secref{prompt-design} below). The expression is validated through a
closed loop program synthesis step which checks that it is well-formed and evaluates to the target fragment
$s$. If this process succeeds, the system replaces the selected substring $s$ with the interpolation
expression \kw{\{$e$\}}, creating a new document configuration. This is the primary successful path through
the workflow and returns the system to the entry state where it is waiting for another top-level interaction
from the author.

\end{enumerate}
